The \project{unRAVE} catalog

### 2016-09-08 article/unrave.tex
Add hot stars figure
Update globular cluster figure #29

\begin{figure*}[p]
\includegraphics[width=\textwidth]{figures/HRD_GCs.pdf}
\caption{Top panels: Effective temperature $\teff$ and surface gravity $\logg$ from this work for prescribed members of globular clusters from \citet{Kunder_2014,Anguino_2015}. Bottom Panels: The same stars are shown as per the top panels, where $\teff$ and $\logg$ have been sourced from the fourth \rave\ data release. A representative Padova \citep{Bressan_2012} isochrone is shown for each cluster in each panel.
\label{fig:globular-cluster-HRD}}
\end{figure*}

@@

\begin{figure}[p]
\center
%\includegraphics[width=0.65\textwidth]{figures/hot-stars.pdf}
\caption{Effective temperatures $\teff$ and surface gravities $\logg$ from this work, where each hexagonal bin is colored by the \emph{maximum} temperature for any star in that bin, as reported by the \rave\ pre-processing pipeline \texttt{SPARV}.  Hot stars are not included in our training set, and appear above the turnoff in our labels.  For this reason, we supply a boolean quality control flag \texttt{QC} that flags stars with $\teff > 8000$~K (as reported by \texttt{SPARV}), and other results that are known to be erroneous.\label{fig:hot-stars}}
\end{figure}

>>>>

\begin{figure*}[p]
\center
\includegraphics[height=\textheight]{figures/globular-clusters.pdf}
\caption{Effective temperature $\teff$ and surface gravity $\logg$ for globular cluster members identified by \citet{Kunder_2014,Anguiano_2015}.  Left-hand panels indicate results from the fourth \rave\ data release \citep{Kordopatis_2013}, and the right-hand panels show results from this work. A representative isochrone is shown for each cluster \citep{Bressan_2012}.\label{fig:globular-cluster-HRD}}
\end{figure*}

@@

\begin{figure}[p]
\center
\includegraphics[width=0.65\textwidth]{figures/hot-stars.pdf}
\caption{Effective temperatures $\teff$ and surface gravities $\logg$ from this work, where each hexagonal bin is colored by the \emph{maximum} temperature for any star in that bin, as reported by the \rave\ pre-processing pipeline \texttt{SPARV}.  Hot stars are not included in our training set, and appear above the turnoff in our labels.  For this reason, we supply a boolean quality control flag \texttt{QC} that flags stars with $\teff > 8000$~K (as reported by \texttt{SPARV}), and other results that are known to be erroneous.\label{fig:hot-stars}}
\end{figure}
